Tsbrowse: a genome browser for Ancestral Recombination Graphs

### 2025-04-22 manuscript/cover_letter.tex
Update manuscript/cover_letter.tex
Co-authored-by: Jerome Kelleher <jk@well.ox.ac.uk>

    The manuscript describes an open-source Python web-app to visualise
    fundamental
    entities
    of Ancestral Recombination Graphs (ARGs). ARGs are a topic of intense
    research
    interest and
    have revolutionised the field of genomics following recent technological
    advancements
    which have made their inference from large-scale empirical datasets
    possible: see Grundler et al. (Science, 2025), Speidel et al. (Nature,
    2025)
    for recent ARG-based findings, and Nielsen et al. (Nature Reviews Genetics,
    2024) for a recent review of ARG inference.

>>>>

    The manuscript describes an open-source Python web-app to visualise
    fundamental
    entities
    of Ancestral Recombination Graphs (ARGs). ARGs are a topic of intense
    research
    interest in the field of genomics, following recent technological
    advancements
    which have made their inference from large-scale empirical datasets
    possible: see Grundler et al. (Science, 2025), Speidel et al. (Nature,
    2025)
    for recent ARG-based findings, and Nielsen et al. (Nature Reviews Genetics,
    2024) for a recent review of ARG inference.
